Hierarchical Reverberation Mapping

### 2013-11-01 Paper/ms.tex
Mention true values
Slight editing to conclusions

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution is indicated by the white star symbol.\label{fig:posterior}}
\end{center}
\end{figure}

@@

\section{Conclusions}\label{sec:conclusions}
Reverberation mapping is an important, yet observationally intensive,
technique in studies of active galaxies. This has motivated substantial
research into RM data analysis techniques, as well as less costly observing
strategies. The recent approach of \citet{2012MNRAS.427.2701F} demonstrated
that it is possible to combine information from many sparsely-measured AGN
and infer properties of the sample rather than insisting on accurate results
about a particular object.

>>>>

\begin{figure}
\begin{center}
\includegraphics[scale=0.5]{Figures/posterior.eps}
\caption{The joint posterior distribution for $\mu$ and $\sigma$, hyperparameters
describing the distribution of $\bar{\tau}$ values in the sample. The prior
distribution was uniform over the area shown.
The true solution $(\mu = 0.867, \sigma = 0.157)$
is indicated by the white star symbol.\label{fig:posterior}}
\end{center}
\end{figure}

@@

\section{Conclusions}\label{sec:conclusions}
Reverberation mapping campaigns are observationally intensive, yet potentially
very informative. This has led to
research into RM data analysis techniques, as well as less costly observing
strategies. The recent approach of \citet{2012MNRAS.427.2701F} demonstrated
that it is possible to combine information from many sparsely-measured AGN
and infer properties of the sample rather than insisting on accurate results
about a particular object.
